\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using a Shared Input

### 2018-01-30 journalWallFriction/experiment.tex
more todos on the paper.  It is missing things!

%\emph{Hardware Demonstration: Position Control of n Robots}\\
%A hardware setup with a bounded platform, magnetic sliders, and a magnetic guide board was used to implement  Alg. \ref{alg:PosControlNRobots}. 
% % Designs for each are available at \cite{Arun2016Thingiverse}. 
%  The pink boundary is toothed with a white free space, as shown in Fig \ref{fig:construction2d}.
%    Only discrete, 1 cm moves in the $x$ and $y$ directions are used. The goal configuration highlighted in the top right corner represents a `U' made of seven particles. The dark red configuration is the current position of the particles. 
%Due to the discretized movements allowed by the boundary, drift moves follow a 1 cm square.  Free particles return to their start positions but particles on the boundary to move laterally, generating a net sliding motion.
%
%Fig. \ref{fig:construction2d} follows the motion of the particles through iterations  $k$=1, 2, and 7. All particles receive the same control inputs, but boundary interactions break the control symmetry.  Particles reach their goal positions in a first-in, first-out arrangement beginning with the bottom-left particle from the staging zone occupying the top-right position of the build zone.
%

>>>>

To demonstrate Alg. XX experimentally, we performed several tests.
Each used the same magnetic setup.
 Two different intestine models were employed, the first a 3D-printed cross-section representation of a small intestine, and the second bovine small intestine.

 \subsection{Magnetic Manipulation Setup}
 explain the magnetic field strength used, the camera system (briefly)

todo: image of the magnetic setup with scale bar
explain the particles used

explain the fluid used in the model.

\subsection{Intestine Phantom Model}

methodology: we used xx material, built a model xx big

todo: snapshots of the the beads in the model, moving toward goal.  We can add lots of annotations.  Fake this series so we have an image for now.

\subsection{Bovine Intestine Cross-section}
todo: procedure for fixating the Bovine tissue sample,
discussion of the challenges

todo: snapshots of the the beads in the model, moving toward goal.  We can add lots of annotations.  Fake this series so we have an image for now.

### 2018-01-30 journalWallFriction/theory2robAlgs.tex
more todos on the paper.  It is missing things!

 We define a $\Delta$ configuration space as a circular shape that considers all possible $\Delta p$s. We also show the starting and ending relative distance as $\Delta s$ and $\Delta e$ in $\Delta$ configuration space in Fig.~\ref{fig:deltaSpace}. Reachable set is the part of $\Delta$ configuration space where if one robot touches a wall in a specific location, the other robot can make the required relative distance without causing touching robot to move. To compute reachable set for circular workspace, first we considered all passible hitting point locations in the workspace. 
 The set of boundary points that a robot can touch before the  other robot  touches is an arc of angle $2(\pi - \frac{\arcsin{d}}{r})$, where $d= |s_1 - s_2|$ and $r$ is the radius of the circle.
 %Here $\alpha$ is the arc of the circle that it is not possible to keep the current relative distance while one robot is touching the wall in that point and is defined by $\alpha = 2 \sin ^{-1}(d)$. 
 We define the angle between two particles as $\theta = \arctan(\frac{p_1.x-p_2.x}{p_1.y - p_2.y})$.

\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{reachableSetCircle.pdf}\end{overpic}
\caption{\label{fig:deltaSpace}Left:  the set of points where the red robot is the first to contact the boundary are drawn with a red arc. The  set of points where the blue robot is the first to contact the boundary are drawn with a blue arc. 
The possible points for the blue and pink particles to touch the boundary is shown in blue and pink arcs. Right: When the blue particle is touching a wall (blue square) the other particle (pink square) can go anywhere in the reachable set (blue region).}
\end{figure}

@@

There are infinite reachable sets, parameterized by first contact location $\psi$, as shown in Fig.~\ref{fig:regionMove}.
%We make the reachable sets by knowing the angle of the chord, $\psi$, shown in Fig.~\ref{fig:psigamma}. Minimum and maximum values of $\psi$ can be calculated in the following equation.
\begin{align}
 \psi \in \Big(\theta +\frac{\sin^{-1}{d}}{2r} - \frac{\pi}{2}, \theta -\frac{\sin^{-1}{d}}{2r} + \frac{\pi}{2}\Big)
% \psi_{\max} &= \theta -\frac{\alpha}{2} + \frac{\pi}{2}
\end{align}
$\gamma$ is half the angle of the arc that the reachable set's chord has shown in Fig.~\ref{fig:deltaSpace} and is calculated by:
\begin{align}
p_\psi &= r[\cos(\psi ), \sin(\psi )]\\
d_\perp&= 2 \abs{(s_1.p_\psi - s_2.p_\psi)}\\
\gamma &= \cos^{-1} \Big(1-\frac{d_\perp}{r} \Big)
\end{align}
Reachable sets with $\pi$ difference in $\psi$ value are equivalent in the  $\Delta$ configuration space, so we can plan in this space and choose to immobilize the particle closest to a wall.

The equation for the four lines outlining the reachable set can be found as follows:

\begin{align}\label{eq:circlereachable}
l_1 &=  r \Big((\cos\psi_{\min}, \sin\psi_{\min})\\ \nonumber
& - (\cos(\gamma_c + \psi_{\min}), \sin(\gamma_c + \psi_{\min}))\Big) &  0<\gamma_c< \gamma_{\psi_{\min}},\\ \nonumber
l_2 &=  r \Big((\cos\psi_{\max}, \sin\psi_{\max})\\ \nonumber
& - (\cos(\gamma_c + \psi_{\max}), \sin(\gamma_c + \psi_{\max}))\Big) &  \gamma_{\psi_{\max}}<\gamma_c< 0,\\  \nonumber
l_3 &=  r \Big((\cos\psi, \sin\psi)\\ \nonumber
& - (\cos( \psi+\gamma_c ), \sin( \psi+ \gamma_c))\Big) &  \psi_{\min}<\psi< \psi_{\max},\\ \nonumber
l_4 &=  r \Big((\cos\psi, \sin\psi)\\ \nonumber
& - (\cos( \psi-\gamma_c ), \sin( \psi- \gamma_c))\Big) &  \psi_{\min}<\psi< \psi_{\max}.\\ \nonumber
\end{align}
We combine these boundaries to make the reachable set. 
The algorithm first makes the reachable set, and then checks if the goal relative position is in the reachable set. If it is not in the reachable set, the closest point on the reachable set from $\Delta g$ would be our current goal. We need to find a $\psi$ that would enable us to reach to the required relative goal distance. To do so, we first check $\psi_{min}$ and $\psi_{max}$. \eqref{eq:ifinchord} shows if any point $p$, is in the region made by the robots if the touching robot has the angle $\psi$.

@@

Here $c$ is coordinate of the circle and $r$ is the radius of the workspace.
 If $\Delta g$ is not in the region made by $\psi_{\min}$ or $\psi_{\max}$, we draw a line from $\Delta g$ and the current relative position, $\Delta s$. This line is a chord of the circle and we find the $\psi$ that makes this region. Now that $\psi$ is found, we move the particles to make the current goal. If current goal is our final goal, we go to the final goal position. If it is not our final goal, we continue to set the closest point on the reachable set to our current goal until we reach the goal. 
% When a particle contacts a wall, the other particle can move to any position in the reachable set while the first robot is immobile. 
%Two reachable sets are possible, horizontal and vertical. 
%Each non-slip move changes the $\Delta$ configuration space, as shown in  Fig.~\ref{fig:regionMove}.

@@

\begin{algorithm}[htb]
\caption{ { \sc 2-ParticlePathPlanning}($s_1,s_2,g_1,g_2,P$)}\label{alg:optimalAlg}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two robots. 
%$(0,0)$ is bottom corner,
 $P$ is a list of the vertices of a convex polygon. 
% \emph{PathList} contains all the paths sorted by their path length plus an admissible heuristic. 
% \State  \emph{PathList} $\gets \{\}$
 \State $(p_1,p_2) \gets (s_1,s_2) $
 \State $R \gets   \{ p_1,p_2,g_1,g_2  ,moves\} $ \Comment $R$ contains the current robot positions, the goal positions, and the move sequence
 \State $\Delta p \gets p_2-p1$
 \State $\Delta g \gets g_2-g_1$
\While {$|\Delta g| < |\Delta p|+ \epsilon$}  %R.p_1 \ne g_1$ \textbf{and} $R.p_2 \ne g_2$}
\State Calculate the reachable set using \eqref{eq:circlereachable} or Fig.~\ref{fig:polygonAlg}
\State $ \Delta cg\gets $nearest point on the reachable set to $\Delta g$
\State Add the required moves to $moves$ for the particles to achieve $\Delta cg$ 
%\For{ $\theta \in \{0^\circ, 90^\circ, 180^\circ, 270^\circ \}$ }
%\State $(r_1,r_2,g_1,g_2) \gets$ {\sc Rotate}($R.r_1,R.r_2,g_1,g_2,\theta$)
%\State $\{d, $ \parbox[t]{.3\linewidth}{%
% \emph{moves,}$ r_1,r_2\} \gets$\\
 %{\sc  PlanMoveUp}($r_1,r_2,g_1,g_2,L, P.\text{\emph{moves}}$)}
%\State $(\text{\emph{moves}}, r_1,r_2) \gets$ {\sc Rotate}(\emph{moves}$, r_1,r_2,-\theta$)
%\State   {\sc Push} $\{d, \text{\emph{moves}}, r_1,r_2\} $ onto \emph{PathList}
%\EndFor
%\State {\sc Sort}(\emph{PathList}) \Comment sort by admissible heuristic
%\State $R \gets $ {\sc Pop} first element of \emph{PathList}
\EndWhile
\State $moves \gets moves+ {g_2 - p2}$
\State \Return \emph{moves}
\end{algorithmic}
\end{algorithm}

@@

Extending path planning to 3D is possible only if the two particles do not initially have the same $x$ and $y$ positions.
For ease of analysis, we assume the workspace boundaries extend in the $\pm z$ direction to form either right cylinders or right prisms.
If the 3D projection is at a different angle, redefine the 2D workspace as a region perpendicular to the projection.
 First, we move the closest particle to the boundary, which prevents its $z$ coordinate from changing.  
 We next apply actuation in either the $\pm z$ direction to achieve the desired $\Delta z$.
 Then the particles are actuated away from the boundary and to the appropriate $z$ positions.
 Path planning continues using Alg. XX to position the particles to the desired $x$ and $y$ positions. 
 As an example, consider Fig.~\ref{fig:zaxis} which shows a cylinder.
 The blue particle starts in the blue disk and the red particle starts in the red disk. There are two possible optimal paths shown with parallel arrows. 
Each arrow will cause one of the particles to touch the wall, enabling the other robot to move freely in the  $z$ axis to achieve the required relative position.
This can be extended to other 3D workspaces if the workspace can be locally approximated as a 3D prism or cylinder. Other workspaces may be better handled by other path planners, such as \cite{MassiveUnifromManipulation}.

>>>>

 We define a $\Delta$ configuration space as a circular shape that considers all possible $\Delta p$s. We also show the starting and ending relative distance as $\Delta s$ and $\Delta e$ in $\Delta$ configuration space in Fig.~\ref{fig:regionMove}. Reachable set is the part of $\Delta$ configuration space where if one robot touches a wall in a specific location, the other robot can make the required relative distance without causing touching robot to move. To compute reachable set for circular workspace, first we considered all passible hitting point locations in the workspace. 
 The set of boundary points that a robot can touch before the  other robot  touches is an arc of angle $2(\pi - \frac{\arcsin{d}}{r})$, where $d= |s_1 - s_2|$ and $r$ is the radius of the circle.
 %Here $\alpha$ is the arc of the circle that it is not possible to keep the current relative distance while one robot is touching the wall in that point and is defined by $\alpha = 2 \sin ^{-1}(d)$. 
 We define the angle between two particles as $\theta = \arctan(\frac{p_1.x-p_2.x}{p_1.y - p_2.y})$.

\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{reachableSetCircle.pdf}\end{overpic}
\caption{\label{fig:regionMove}Left:  the set of points where the red robot is the first to contact the boundary are drawn with a red arc. The  set of points where the blue robot is the first to contact the boundary are drawn with a blue arc. 
The possible points for the blue and pink particles to touch the boundary is shown in blue and pink arcs. Right: When the blue particle is touching a wall (blue square) the other particle (pink square) can go anywhere in the reachable set (blue region).}
\end{figure}

@@

There are infinite reachable sets, parameterized by first contact location $\psi$, as shown in Fig.~\ref{fig:regionMove}.
%We make the reachable sets by knowing the angle of the chord, $\psi$, shown in Fig.~\ref{fig:psigamma}. Minimum and maximum values of $\psi$ can be calculated in the following equation.
\begin{align}
 \psi \in \Big(\theta +\frac{\sin^{-1}{d}}{2r} - \frac{\pi}{2}, \theta -\frac{\sin^{-1}{d}}{2r} + \frac{\pi}{2}\Big)
% \psi_{\max} &= \theta -\frac{\alpha}{2} + \frac{\pi}{2}
\end{align}
$\gamma$ is half the angle of the arc that the reachable set's chord has shown in Fig.~\ref{fig:regionMove} and is calculated by:
\begin{align}
p_\psi &= r[\cos(\psi ), \sin(\psi )]\\
d_\perp&= 2 \abs{(s_1.p_\psi - s_2.p_\psi)}\\
\gamma &= \cos^{-1} \Big(1-\frac{d_\perp}{r} \Big)
\end{align}
Reachable sets with $\pi$ difference in $\psi$ value are equivalent in the  $\Delta$ configuration space, so we can plan in this space and choose to immobilize the particle closest to a wall.

The equation for the four lines outlining the reachable set can be found as follows:
\todo{place x terms and y terms together (reduce the parenthesis)}
\begin{align}\label{eq:circlereachable}
l_1 &=  r \Big((\cos\psi_{\min}, \sin\psi_{\min})\\ \nonumber
& - (\cos(\gamma_c + \psi_{\min}), \sin(\gamma_c + \psi_{\min}))\Big) &  0<\gamma_c< \gamma_{\psi_{\min}},\\ \nonumber
l_2 &=  r \Big((\cos\psi_{\max}, \sin\psi_{\max})\\ \nonumber
& - (\cos(\gamma_c + \psi_{\max}), \sin(\gamma_c + \psi_{\max}))\Big) &  \gamma_{\psi_{\max}}<\gamma_c< 0,\\  \nonumber
l_3 &=  r \Big((\cos\psi, \sin\psi)\\ \nonumber
& - (\cos( \psi+\gamma_c ), \sin( \psi+ \gamma_c))\Big) &  \psi_{\min}<\psi< \psi_{\max},\\ \nonumber
l_4 &=  r \Big((\cos\psi, \sin\psi)\\ \nonumber
& - (\cos( \psi-\gamma_c ), \sin( \psi- \gamma_c))\Big) &  \psi_{\min}<\psi< \psi_{\max}.\\ \nonumber
\end{align}
We combine these boundaries to make the reachable set. 
The algorithm first makes the reachable set, and then checks if the goal relative position is in the reachable set. If it is not in the reachable set, the closest point on the reachable set from $\Delta g$ would be our current goal. We need to find a $\psi$ that would enable us to reach to the required relative goal distance. To do so, we first check $\psi_{min}$ and $\psi_{max}$. \eqref{eq:ifinchord} shows if any point $p$, is in the region made by the robots if the touching robot has the angle $\psi$.

@@

Here $c$ is coordinate of the circle and $r$ is the radius of the workspace.
 If $\Delta g$ is not in the region made by $\psi_{\min}$ or $\psi_{\max}$, we draw a line from $\Delta g$ and the current relative position, $\Delta s$. This line is a chord of the circle and we find the $\psi$ that makes this region. Now that $\psi$ is found, we move the particles to make the current goal. If current goal is our final goal, we go to the final goal position. If it is not our final goal, we continue to set the closest point on the reachable set to our current goal until we reach the goal.

 \todo{  how do we find the collision point }

% When a particle contacts a wall, the other particle can move to any position in the reachable set while the first robot is immobile. 
%Two reachable sets are possible, horizontal and vertical. 
%Each non-slip move changes the $\Delta$ configuration space, as shown in  Fig.~\ref{fig:regionMove}.

@@

\begin{algorithm}[htb]
\caption{ { \sc 2-ParticlePathPlanning}($s_1,s_2,g_1,g_2,P$)}\label{alg:optimalAlg}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
%$(0,0)$ is bottom corner,
 $P$ is a list of the vertices of a convex polygon. 
% \emph{PathList} contains all the paths sorted by their path length plus an admissible heuristic. 
% \State  \emph{PathList} $\gets \{\}$
 \State $(p_1,p_2) \gets (s_1,s_2) $
\State  moves $\gets \{\}$
 \State $R \gets   \{ p_1,p_2,g_1,g_2  ,\textrm{moves}\} $ \Comment $R$ contains the current robot positions, the goal positions, and the move sequence
 \State $\Delta p \gets p_2-p_1$
 \State $\Delta g \gets g_2-g_1$
\While {$|\Delta g| < |\Delta p|+ \epsilon$}  %R.p_1 \ne g_1$ \textbf{and} $R.p_2 \ne g_2$}
\State $R_s$ = Compute reachable set  \Comment use \eqref{eq:circlereachable} or Fig.~\ref{fig:polygonAlg}
\State $ \Delta g_c\gets $nearest point in $R_s$ to $\Delta g$
\State  add move to hit the wall
\State  add move to reach  $ \Delta g_c$
\State Add the required moves to $moves$ for the particles to achieve $\Delta g_c$ 
%\For{ $\theta \in \{0^\circ, 90^\circ, 180^\circ, 270^\circ \}$ }
%\State $(r_1,r_2,g_1,g_2) \gets$ {\sc Rotate}($R.r_1,R.r_2,g_1,g_2,\theta$)
%\State $\{d, $ \parbox[t]{.3\linewidth}{%
% \emph{moves,}$ r_1,r_2\} \gets$\\
 %{\sc  PlanMoveUp}($r_1,r_2,g_1,g_2,L, P.\text{\emph{moves}}$)}
%\State $(\text{\emph{moves}}, r_1,r_2) \gets$ {\sc Rotate}(\emph{moves}$, r_1,r_2,-\theta$)
%\State   {\sc Push} $\{d, \text{\emph{moves}}, r_1,r_2\} $ onto \emph{PathList}
%\EndFor
%\State {\sc Sort}(\emph{PathList}) \Comment sort by admissible heuristic
%\State $R \gets $ {\sc Pop} first element of \emph{PathList}
\EndWhile
\State $moves \gets moves+ {g_2 - p_2}$  \Comment translate to goal
\State \Return \emph{moves}
\end{algorithmic}
\end{algorithm}

@@

Extending path planning to 3D is possible only if the two particles do not initially have the same $x$ and $y$ positions.
For ease of analysis, we assume the workspace boundaries extend in the $\pm z$ direction to form either right cylinders or right prisms.
If the 3D projection is at a different angle, redefine the 2D workspace as a region perpendicular to the projection.
 First, we move the closest particle to the boundary, which prevents its $z$ coordinate from changing.  
 We next apply actuation in either the $\pm z$ direction to achieve the desired $\Delta z$.
 Then the particles are actuated away from the boundary and to the appropriate $z$ positions.
 Path planning continues using Alg. XX to position the particles to the desired $x$ and $y$ positions. 
 As an example, consider Fig.~\ref{fig:zaxis} which shows a cylindrical workspace.
 The blue particle starts in the blue disk and the red particle starts in the red disk. 
 The two candidate shortest-length paths that touch the wall are shown with parallel arrows. 
Each arrow will cause one of the particles to touch the wall, enabling the other robot to move freely in the  $z$ axis to achieve the required relative position.
This can be extended to other 3D workspaces if the workspace can be locally approximated as a 3D prism or cylinder. Other workspaces may be better handled by other path planners, such as \cite{AaronManipulation2013}, which used  collisions with  protrusions of the workspace to rearrange particles.
